### 2020-06-04 Strings2020/strings6/strings6.tex
Add strings6 [WIP], check CI for thermal3 bug

% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
%% !TeX TS-program = lualatex
%%% LuaLaTeX is required for `tikz-feynman`

@@

\newcommand{\hwNumber}{5}

@@

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
\newcommand{\zbar}{\bar{z}}
\usepackage{tikz-feynman,cancel}

@@

	\item \textbf{Partition Function for Compact Scalars}

>>>>

% !TeX encoding = UTF-8
% !TeX spellcheck = en_US
% !TeX TXS-program:bibliography = biber -l zh__pinyin --output-safechars %
% !TeX TS-program = xelatex
%%% LuaLaTeX is required for `tikz-feynman`

@@

\newcommand{\hwNumber}{6 [WIP]}

@@

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
\newcommand{\zbar}{\bar{z}}
%\usepackage{tikz-feynman,cancel}

\newcommand{\NS}{\ensuremath{\mrm{NS}}}
\newcommand{\R}{\ensuremath{\mrm{R}}}

@@

	\item \textbf{Type 0 Superstrings}

	A closed superstring theory consists of sectors labeled by the boundary conditions of $(\psi,\tilde{\psi})$ along with suitable GSO projections $(-1)^F = \pm 1$. Here we follow the discussions of \textit{Polchinski}, with $\mrm{R}\colon \alpha = 1$ and $\mrm{NS}\colon \alpha = 0$.

	There are also some consistency conditions: by modular invariance, there must be at least one left-moving R sector and at least one right-moving R sector; on the other hand, the OPE must close, and since $\mrm{R} \times \mrm{R} = \mrm{NS}$ there must be corresponding NS sector for each R sector.

	If we includes only the (NS, NS) and the (R, R) sectors, then both must exist due to the above conditions. In fact, closure of OPE implies that the (\,NS$+$, NS$+$) sector must exist. In addition, NS$-$ sector must be paired with another NS$-$ sector due to the level matching condition of the closed string, i.e. it is possible to have a (\,NS$-$, NS$-$) sector.

	The full possiblities can be generated by enumerating all possible (R, R) sectors (there is $2\times 2 = 4$ of them), while applying an extra consistency check that all pairs of vertex operators $O_1,O_2$ are mutually local, i.e.
	\begin{equation}
		\exp i\pi \pqty{
				  F_1 \alpha_2
				- F_2 \alpha_1
				- \tilde{F}_1 \tilde{\alpha}_2
				+ \tilde{F}_2 \tilde{\alpha}_1
			}
		= 1
	\end{equation}
	If $O_1 \in (\,\NS+, \NS+)$, then we have $\alpha_1 = \tilde{\alpha}_1 = 0 = F_1 = \tilde{F}_1$, hence the above factor is always trivial; for $O_1 \in (\R,\R)$, however, $\alpha_1 = \tilde{\alpha}_1 = 1$, which yields a non-trivial constraint for the second operator: $
		F_2 - \tilde{F}_2
		= F_1 \alpha_2 - \tilde{F}_1 \tilde{\alpha}_2
		= \alpha_2 \pqty\big{F_1 - \tilde{F}_1}
		\ (\mop{mod} 2)
	$, assuming $\alpha_2 = \tilde{\alpha}_2$. With $\alpha_2 = 0$ this gives $F_2 = \tilde{F}_2$, and with $\alpha_2 = 1$ this gives $
		F_2 - \tilde{F}_2
		= F_1 - \tilde{F}_1
	$, which means that all (R, R) sectors have the same sign difference between $F$ and $\tilde{F}$. The possible solutions can then be narrowed down to:
	\begin{gather}
		\mrm{0A}\colon\ %
			(\,\NS+,\NS+),\ %
			(\,\NS−,\NS−),\ %
			(\,\R+,\R-),\ %
			(\,\R−,\R+), \\
		\mrm{0B}\colon\ %
			(\,\NS+,\NS+),\ %
			(\,\NS−,\NS−),\ %
			(\,\R+,\R+),\ %
			(\,\R−,\R−), \\
		\text{And additionally, $(\,\NS+,\NS+)$ with any \textit{single one} of the 4 possible (R, R) sectors.}
	\end{gather}

	If there are two (R, R) sectors, then there must be an acompanying $(\,\NS−,\NS−)$ sector due to the closure of OPE. It is straight-foward to check that these possiblilities are all valid under the above constaints: (0) level matching of closed strings, (1) mutual locality, (2) closure of OPE, and (3) (apparent) modular invariance (not sufficient yet, to be checked below).

	\begin{enumerate}
	\item The torus partition function of the theory breaks up into a product of independent sums over the bosonic $X$ and fermionic $(\psi,\tilde{\psi})$ oscillators. The bosonic part is identical to the bosonic string situation, therefore modular invariant; to check the total partition function for modular invariance, we will look at the fermionic contributions $Z = Z_{\psi,\tilde{\psi}}$ explicitly.

	Similar to the Type II case, the building block of $Z$ is given by:
	\begin{equation}
		Z\id{^\alpha_\beta}
		= \Tr_\alpha \bqty{
				(-1)^{\beta F} q^H
			}
	\end{equation}
	Where $\alpha,\beta$ labels the periodicity in the spatial and temporal directions ($\sigma^1,\sigma^2$); note that for fermionic fields, anti-periodicity in the time direction gives the simple trace, while the periodic path integral gives the trace weighted by $(−1)^F̂$, as is explained in \textit{Polchinski}, Appendix A. 
	\end{enumerate}

	\legacyReference
